Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-28 sections/discussion.tex
elaborated on the example

% examples.
In some cases, similarity and dissimilarity failed to measure the usefulness of the comment,
due to the same word being used in a different context.
For example, consider this excerpt from the commit message: \emph{``In the no-assert case, make Q\_ASSERT decay to Q\_ASSUME. I can confirm
better code generation with GCC at least.''}
This comment, \emph{``I'll study the generated code a bit more,''} is not technically contributing, but is classified as a useful comment, which may be because of the word \emph{generate} appears both documents.

>>>>

% examples.
In some cases, similarity and dissimilarity failed to measure the usefulness of the comment,
due to the same word being used in a different context.
For example, consider this excerpt from the commit message: \emph{``In the no-assert case, make Q\_ASSERT decay to Q\_ASSUME. I can confirm
better code generation with GCC at least.''}
This comment, \emph{``I'll study the generated code a bit more,''} is just an author's response, and thus is not technically contributing. However, it is classified as a useful comment. This may be caused by the word \emph{generate} which appears in both documents.
